sensi_an_rotations201911. To analyse rotation runs for paper

### 2019-11-06 inst/documents/sensi_an_rotations201911.Rmd
add new output files

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
  library(rotations)
  library(ggplot2)
  library(gridExtra)

  # where the rotation runs saved
  infolder <- "C:\\Dropbox\\resistanceResults\\rotations\\"
```

@@

# load the data, start with just one experiment
# dataframes will need to be renamed because they will all be called df_res_all to start
infile <- "df_res_all_rot_mig1000.rda"
infile <- paste0(infolder, infile)

>>>>

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
  library(rotations)
  library(ggplot2)
  library(gridExtra)
  library(tidyverse)

  # where the rotation runs saved
  #infolder <- "C:\\Dropbox\\resistanceResults\\rotations\\"
  infolder <- "C:\\Dropbox\\2017_Rotations for IRM\\SJ_Runs_Nov\\"

@@

# load the data, start with just one experiment
# dataframes will need to be renamed because they will all be called df_res_all to start

infile <- "2019-11-05-10-42-df_res_all_rotA210000.rda"

infile <- paste0(infolder, infile)
